---
title: "Batch-rename files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Batch-rename files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r pkgs, message=FALSE, warning=FALSE}
library(gerp)
library(purrr)
library(fs)
library(dplyr)
```

This vignette covers the `ger_batch_rename()`--a function that gives you the ability to rename a folder of files in [standardized format.](https://www.slideshare.net/milkers/naming-things) 

## Test files

A folder of `filenames` are available in the `gerp` package to demonstrate (below we'll copy them to a temporary folder)

```{r dir_copy-tmp_files, eval=TRUE}
tmp_dir <- tempdir()
tmp_files <- fs::as_fs_path(paste0(tmp_dir, "/", "filenames"))
# copy
fs::dir_copy(
  path = system.file("filenames", package = "gerp"), 
  new_path = tmp_files)
```

Confirm this with `fs::dir_tree()`

```{r}
# confirm
fs::dir_tree(tmp_dir)
```

## `ger_batch_rename()`

The files in the temporary `filenames/` folder are a mess, and I want to rename them using a [standardized format](https://www.slideshare.net/milkers/naming-things). Renaming files manually can be time-consuming, so I've written a handy function that will get you 90% there (and pull all the files in a standardized format): 

* all file names are converted to [lower snakecase](https://www.wikiwand.com/en/Snake_case)  

* all punctuation and special characters have been removed from file names  

* file names have a date prefix (the `birth` date, but other options include `"modification"`, `"access"`, or `"change"`)

I'll demonstrate below:

```{r ger_batch_rename}
gerp::ger_batch_rename(path = tmp_files, prefix = "birth")
```

And confirm with `fs::dir_tree()` 

```{r confirm-ger_batch_rename}
# confirm
fs::dir_tree(tmp_dir)
```

```{r , echo=FALSE}
unlink(tmp_dir, recursive = TRUE, force = TRUE)
```

The following sections of this vignette walk through each step to give a better picture of how `ger_batch_rename()` works.

<br>

# Step by step

I'll create another `tmp_files` path with the original (messy) file names:

```{r dir_copy-tmp_files-again, eval=TRUE}
tmp_dir <- tempdir()
tmp_files <- fs::as_fs_path(paste0(tmp_dir, "/", "filenames"))
# copy
fs::dir_copy(
  path = system.file("filenames", package = "gerp"), 
  new_path = tmp_files)
```

And confirm this with `fs::dir_tree()`

```{r confirm-tmp_dir-again}
# confirm
fs::dir_tree(tmp_dir)
```

## Get tibble of file names

`get_files_tbl()` creates a tibble of file paths, names, and date variables:

```{r get_files_tbl, echo=FALSE}
get_files_tbl <- function(path, ...) {
  
  all_files <- fs::dir_info(path = path, ..., type = "file")
  
  file_tbl <- dplyr::mutate(all_files, 
    file_path = as.character(path),
    file_folder = as.character(fs::path_dir(path)),
    file_full_name = as.character(basename(path)),
    file_extension = paste0(".", tools::file_ext(file_full_name)),
    file_name = tools::file_path_sans_ext(file_full_name))
  
  date_tbl <- dplyr::mutate(file_tbl, 
    dplyr::across(dplyr::contains('time'), lubridate::as_date))
  
  files_tbl <- dplyr::select(date_tbl, dplyr::starts_with('file'),
    modification = modification_time, 
    access = access_time, 
    change = change_time, 
    birth = birth_time)
  
  return(files_tbl)
  
}
```

```{r files_tmp}
files_tmp <- get_files_tbl(path = tmp_files)
glimpse(files_tmp)
```

```{r}
files_tmp$file_full_name[1]
```

## Date prefix

Decide which date to use (`"modification"`, `"access"`, `"change"`, or `"birth"`)

```{r get_date_prefix, echo=FALSE}
get_date_prefix <- function(files, time_prefix = "birth") {
  prefixes <- c("modification", "access", "change", "birth")
  if (time_prefix %in% prefixes) {
    
    time_col <- rlang::sym(time_prefix)
    date_prefix_col <- dplyr::mutate(.data = files,
      date_prefix = paste0(!!time_col, "_")
  )
    date_prefix_tbl <- dplyr::select(date_prefix_col, 
      file_path, file_folder, file_full_name, file_extension, file_name, date_prefix)
    return(date_prefix_tbl)
  } else {
    cli::cli_abort(glue::glue("{time_prefix} is not one of the available options"))
  }

}
```

The `date_prefix` column will be added to the cleaned column names. 

```{r file_date_tmp}
file_date_tmp <- get_date_prefix(files = files_tmp)
glimpse(file_date_tmp)
```

```{r}
file_date_tmp$date_prefix[1]
```


## Clean file name 

The `clean_file_name` has been formatted to include the `date_prefix`, lower-snakecase, and all punctuation/special characters have been removed.

```{r get_clean_file_names, echo=FALSE}
get_clean_file_names <- function(df, column) {
  clean_file_names_cols <- dplyr::mutate(df,
    snakes := snakecase::to_snake_case({{column}}),
    hyphens = stringr::str_replace_all(snakes, "[^[:alnum:].]+", "-"),
    clean_file_name = paste0(date_prefix, hyphens, file_extension),
    clean_file_path = paste0(file_folder, "/", clean_file_name)
    # "clean_{{column}}_path" := paste0(date_prefix, hyphens, file_extension)
    )
  
  clean_file_names_tbl <- dplyr::select(clean_file_names_cols, 
    clean_file_name, clean_file_path, file_full_name, file_path)
}
```

```{r clean_tbl}
clean_tbl <- get_clean_file_names(file_date_tmp, file_name)
glimpse(clean_tbl)
```

```{r}
clean_tbl$clean_file_name[1]
clean_tbl$file_full_name[1]
```

**NOTE:** `ger_batch_rename()` can't file the ***content*** of the file names (and you wouldn't want it to).

## Rename all files

Now we place the new and old names in their own vectors and pass them to `rename_all_files()`:

```{r new_names-old_names}
new_names <- clean_tbl[['clean_file_path']]
old_names <- clean_tbl[['file_path']]
```

```{r rename_all_files, echo=FALSE}
rename_all_files <- function(old, new) {
  purrr::walk2(.x = old, .y = new, .f = file.rename)
}
```

```{r use-rename_all_files}
rename_all_files(old = old_names, new = new_names)
```

We can confirm a final time with `fs::dir_tree()`: 

```{r}
fs::dir_tree(tmp_files)
```


```{r , echo=FALSE}
unlink(tmp_dir, recursive = TRUE, force = TRUE)
```

