---
title: "Batch-rename files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Batch-rename files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r pkgs, message=FALSE, warning=FALSE}
library(gerp)
```

This vignette covers `grp_batch_rename()`, a function that gives you the ability to rename a folder of files in a [standardized format.](https://www.slideshare.net/milkers/naming-things)

## Test files

Below we'll create a folder of messy file names in a temporary folder.

```{r create-files}
tmp_files <- file.path(tempdir(), "filenames")
dir.create(tmp_files)
messy <- c(
  "JW7d^(2sl@deletethisandyourcareerisoverWx2.txt",
  "Joe's Filenames Use Space and Punctuation.xlsx",
  "fig 2.png",
  "figure 1.png",
  "myabstract.docx"
)
file.create(file.path(tmp_files, messy))
```

Confirm this with `gerp::grp_path()`

```{r confirm-files}
gerp::grp_path(tmp_files, tree = TRUE)
```

## `grp_batch_rename()`

The files in the temporary `filenames/` folder are a mess, and I want to rename them using a [standardized format](https://www.slideshare.net/milkers/naming-things). Renaming files manually can be time-consuming, so `grp_batch_rename()` will get you 90% there:

* all file names are converted to lowercase words separated by hyphens (the same rules as `grp_fname()`)

* all punctuation and special characters are removed from file names

* file names have a date prefix (the `"modification"` date, but other options include `"birth"`, `"access"`, or `"change"`)

* files that already have a date prefix are skipped

Preview the new names with `dry_run = TRUE`:

```{r dry-run}
preview <- gerp::grp_batch_rename(tmp_files, dry_run = TRUE)
basename(preview$new)
```

Then rename the files:

```{r rename}
gerp::grp_batch_rename(tmp_files)
```

And confirm with `gerp::grp_path()`

```{r confirm-rename}
gerp::grp_path(tmp_files, tree = TRUE)
```

**NOTE:** `grp_batch_rename()` can't change the ***content*** of the files (and you wouldn't want it to).

```{r cleanup, include=FALSE}
unlink(tmp_files, recursive = TRUE)
```
