---
title: "Names"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Names}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r pkg, message=FALSE, warning=FALSE, eval=TRUE}
library(gerp)
```

```{r src, eval=TRUE, include=FALSE}
# source("../R/names.R")
```


# `ger_name()`

> "*It ain't what they call you, it's what you answer to.*" - [W.C. Fields](https://www.goodreads.com/quotes/130631-it-ain-t-what-they-call-you-it-s-what-you-answer) 

The naming functions in `gerp` are modeled around two resources. The names for files and folders come from Jenny Bryan's excellent ['Naming things' slides](https://www.slideshare.net/milkers/naming-things). Names for R objects come from the [`tidyverse` style guide](https://style.tidyverse.org/).

The principles for naming files include: 

1. All file names should be [lower kebab-case](https://en.wikipedia.org/wiki/Naming_convention_(programming)#Delimiter-separated_words), with no white space 

2. A date prefix should be appended to all files for provenance and separated from the file name with an underscore

3. Special characters and punctuation should not be used (but their meanings should be preserved)

Both functions copy the R object name to the clipboard (making it easier to use). 


# `ger_fname()`

`ger_fname()` will convert the text to lower kebab-case and add a date prefix. 

```{r}
ger_fname("My File.txt")
```

```
✔ '2023-04-09_my-file.txt' is copied to the clipboard!
```

It handle's file version numbers and punctuation:

```{r}
ger_fname("01 joe's report .xlsx")
```

```
✔ '2023-04-09_01-joes-report.xlsx' is copied to the clipboard!
```

And special characters:

```{r}
ger_fname("%! Joe's crazy *!$# file name.xlsx")
```

```
✔ '2023-04-09_joes-crazy-file-name.xlsx' is copied to the clipboard!
```

# `ger_name()`

`ger_name()` is designed to return a [tidyverse style](https://style.tidyverse.org/syntax.html#object-names) name for an object (i.e. `vector`, `data.frame`, `tibble`, etc.). 

It works well for file names that have been created with `ger_fname()`:

```{r date-prefix, eval=FALSE}
ger_name("2023-04-09_my-file.txt")
```

```
✔ 'my_file_txt_2023_04_09' is copied to the clipboard!
```

`ger_name()` replaces the following symbols with abbreviations:

```{r all-abbreviations, eval=FALSE}
gerp::ger_name("~ ! @ # $ % ^ & * — = +")
```

```
✔ 'tilde_bang_at_num_dollar_perc_hat_and_ast_emdash_equals_plus' is copied to the clipboard!
```

And reorganizes names with numbers prefixes:

```{r abbreviations, eval=FALSE}
ger_name("20 % of this & that")
```

```
✔ 'perc_of_this_and_that_20' is copied to the clipboard!
```

`ger_name()` converts just about any string of characters into something that can be assigned to R variables.

```{r crazy-names, eval=FALSE}
ger_name("123456 ! bingo + bongo")
```

```
✔ 'bang_bingo_plus_bongo_123456' is copied to the clipboard!
```

To ensure the names aren't too long or repeat terms, `ger_name()` won't repeat symbols. 

```{r no-repeat, eval=FALSE}
gerp::ger_name("... !! ++")
```

```
✔ 'dot_bang_plus' is copied to the clipboard!
```

