---
title: "Good enough names"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Good enough names}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# source("../R/ger_name.R")
```

```{r pkg, message=FALSE, warning=FALSE}
library(gerp)
```

# `ger_name()`

> "*It ain't what they call you, it's what you answer to.*" - [W.C. Fields](https://www.goodreads.com/quotes/130631-it-ain-t-what-they-call-you-it-s-what-you-answer) 


`ger_name()` is designed to return a [tidyverse style](https://style.tidyverse.org/syntax.html#object-names) name for an object (i.e. variable). It works well for file names that have a date prefix: 

```{r date-prefixc, eval=FALSE}
ger_name("1986-10-12_file.txt")
```

```
✔ 'filedot_txt_1986_10_12' is copied to the clipboard!
```

`ger_name()` replaces some symbols with abbreviations:

```{r all-abbreviations, eval=FALSE}
gerp::ger_name("~ ! @ # $ % ^ & * — = +")
```

```
✔ 'tilde_bang_at_num_dollar_perc_hat_and_ast_emdash_equals_plus' is copied to the clipboard!
```

But keeps the characters and words:

```{r abbreviations, eval=FALSE}
ger_name("20 % of this & that")
```

```
✔ 'perc_of_this_and_that_20' is copied to the clipboard!
```

It will also reorganize crazy file names into something that can be assigned to R variables.

```{r crazy-names, eval=FALSE}
ger_name("123456 ! bingo + bongo")
```

```
✔ 'bang_bingo_plus_bongo_123456' is copied to the clipboard!
```

To ensure the names aren't too long or repeat terms, `ger_name()` doesn't repeat symbols. 

```{r no-repeat, eval=FALSE}
gerp::ger_name("... !! ++")
```

```
✔ 'dot_bang_plus' is copied to the clipboard!
```





