---
title: "Naming workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Naming workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r pkgs, eval=TRUE}
library(gerp)
library(tibble)
library(readr)
```

# Naming workflow 

`ger_path()`, `ger_fname()`, and `ger_name()` all work as a team to 1) create reliable names for files and objects, and 2) make it easier to maintain the connection between project files and object names.

## Example 1

`ger_name()` works well for file names that have been located with `ger_path()` and created with `ger_fname()`. 

Assume I have a file named `99$bad%FILE%nAme.xlsx` in my `inst/extdata` folder. I can create a new `bad_file_name.R` script in the `data-raw/` folder: 

```{r}
file.create("data-raw/bad_file_name.R")
```

```
[1] TRUE
```

The follow contents are placed in `bad_file_name.R`

```{r}
# get absolute path
abs_pth <- gerp::ger_path("inst/extdata/99%bad%%FILE%name.csv")
# get relative path for file name
gerp::ger_path("inst/extdata/99%bad%%FILE%name.csv", type = 'rel') |> gerp::ger_fname()
```

```
✔ '2023-04-10_99-bad-file-name.csv' is copied to the clipboard!
```

```{r}
# paste and store file name
exprt_nm <- "2023-04-10_99-bad-file-name.csv"
# get object name 
"2023-04-10_99-bad-file-name.csv" |> gerp::ger_name()
```

```
✔ 'bad_file_name_csv_2023_04_10_99' is copied to the clipboard!
```

```{r}
# paste and import using absolute path
library(readr)
bad_file_name_csv_2023_04_10_99 <- readr::read_csv(file = abs_pth)
# export to new location using file name
readr::write_csv(x = bad_file_name_csv_2023_04_10_99, file = paste0("data-raw/", exprt_nm))
ger_path("data", tree = TRUE)
```

```
/Users/mjfrigaard/projects/my_project/data-raw
└── 2023-04-10_99-bad-file-name.csv
```

## Example 2 

In the event I've created an object in R and need to export it, the workflow is slightly different. 

Assume I've created `new_data`, which I want to store in the `data/` folder:

```{r new_data, eval=TRUE}
new_data <- tibble::tribble(
   ~x,                 ~y,    ~z,
  "J",   3.78788225133507, FALSE,
  "N",   6.79125214331172,  TRUE,
  "T",   3.70527803343078,  TRUE,
  "A",   5.43565140930839,  TRUE,
  "Y",   8.13565077574797, FALSE,
  "M",   6.10749813415254, FALSE,
  "G",    8.2922407776683,  TRUE,
  "B",   2.78855879559163, FALSE,
  "X",   4.36696377700339, FALSE,
  "O",   2.34682208415642,  TRUE
  )
new_data
```

```{r , eval=FALSE}
# store name
exrt_nm <- gerp::ger_fname("new_data")
```

```
✔ '2023-04-10_new-data' is copied to the clipboard!
```

```{r , eval=FALSE}
# paste to check export path
paste0("data/", "2023-04-10_new-data", ".rds")
```

```
[1] "data/2023-04-10_new-data.rds"
```

```{r , eval=FALSE}
# store 
exrt_pth <- paste0("data/", "2023-04-10_new-data", ".rds")
```

```{r export_my_data, eval=FALSE}
# export
readr::write_rds(x = new_data, file = exrt_pth)
ger_path("data", tree = TRUE)
```

```
/Users/mjfrigaard/projects/my_project/data
└── 2023-04-10_new-data.rds
```

